
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Carl Myers
% @author   Carl Harris Myers
% @url      http://www.cmyers.org
% @date     January 2009
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\begin{document}
\name{\Large Carl Harris Myers}
\begin{resume}


    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}\vspace{2mm}

    \begin{tabular}{@{} l @{\hspace{38mm}} r}
    Carl Myers
    & (206) 931-9916 \\
    1614 Summit Ave \#202
    & cmyers@cmyers.org \\
    Seattle, WA 98122
    & http://www.cmyers.org \\
    \end{tabular}


    %____________________________________________________________________________________
    % Objective
    \section{\mysidestyle Objective}

    As a skilled Software Design Engineer, I want to contribute to a company in
    a customer-centric way which makes a significant contribution to my
    employer, and allows me to grow as an engineer.

    %____________________________________________________________________________________
    % Experience
    \section{\mysidestyle Experience}

    {\bf Amazon.com}, Seattle, WA   \hfill {\bf March, 2006 -- January, 2009}
    \vspace{1mm} \\ \vspace{1mm}
    {\sl Software Design Engineer, Developer Applications Team} % \hfill {\bf January, 2008 -- January, 2009}\\
    \begin{list2}
        \vspace*{1mm}
        \item
          Implemented an internal web service which provided string translation and
          localization and delivered the service to customers.  This service replaced
          the previous system and is a key component of the company's international
          websites.  Was lead engineer on a team including 3 other engineers.
        \item
          Performed requirements gathering and design for an internal web service which
          provided string translation and localization.  Wrote design proposal and
          created a data model utilizing an Oracle back-end.
        \item
          Scoped, evaluated, then selected and implemented/integrated third-party text
          translation middleware for use internally, connecting engineers to language
          translators.
    \end{list2}

    \vspace{1mm} \vspace{1mm}%
    {\sl Software Design Engineer, Developer Tools Team} \\% \hfill {\bf January, 2008 -- January, 2009}\\
    \begin{list2}
        \vspace*{1mm}
        \item
          Maintained and supported a complex build system used by over 2000 developers
          which focused on reproducibility, consistency, and dependency management of
          large codebases.  Worked on a codebase which exceeded 200GB and 8 million
          files, which was divided up into more than 13,000 discrete packages.
        \item
          Acted as primary owner of the main source control repository, which included
          migrating to a new machine, upgrading software, ensuring backups were
          functioning, and being responsible for a priceless codebase containing over
          8,000 man-years of work.
        \item
          Designed and implemented an internal-customer-facing distributed application
          which allowed customers to view logs for the build system to assist in
          debugging.
        \item
          Performed porting and developed porting tools to assist in the migration from
          Red Hat Enterprise Linux 3 to Red Hat Enterprise Linux 5.
        \item
          Performed porting and key initial set up for migration from 32-bit Red Hat
          Enterprise Linux 3 to 64-bit Red Hat Enterprise Linux 4 under strict time
          constraints, allowing the company to save millions of dollars on hardware.
        \item
          Worked on many UI improvements which made developer tools easier to use,
          improving developer productivity.
        \item
          Participated in "Environment Improvement Ninjas", an internal group where we
          all spent personal time developing environment improvements to make ourselves
          (and other developers) more productive.  Worked in porting the environment to
          new platforms, writing scripts to get metadata more easily, and tab
          completions.
        \item
          Assisted in porting many shared packages and third-party code from Red Hat 7.2
          to Red Hat Enterprise Linux 3
    \end{list2}

    {\bf Purdue University Robot Vision Lab}, Lafayette, IN  \vspace{2mm}\\\vspace{1mm}%
    {\sl Student Worker} \hfill {\bf 2005}\\
    \begin{list2}
        \vspace*{1mm}
        \item
            Worked with researchers to write and maintain code using and
            supplementing Intel's OpenCV Computer Vision Library.  Employed C,
            C++, Java, and maintained and scripted a complex build process.
    \end{list2} 

    {\bf Purdue University Physics Computer Network}, Lafayette, IN  \vspace{2mm}\\\vspace{1mm}%
    {\sl Student Worker} \hfill {\bf 2004}\\
    \begin{list2}
        \vspace*{1mm}
        \item
            Worked with members of the Physics Department in a help-desk
            environment employing problem-solving and troubleshooting to solve
            both hardware and software problems, including some software
            development.
    \end{list2} 

    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    {\bf Purdue University}, Lafayette, IN \vspace{2mm}
    \begin{list2}
        \vspace*{1mm}
        \item
            Graduated in December of 2005 with a Bachelors in Electrical and
            Computer Engineering.
        \item
            Coursework included Operating Systems Engineering, Advanced Object Oriented
            Programming and Scripting, Object Oriented Design, Networking, Microprocessor
            Architecture.
    \end{list2}

    %____________________________________________________________________________________
    % Achievements
    \section{\mysidestyle Achievements} 

    \begin{list2} 
    \item
        Recognized as a leader in ownership and support of systems including
        on-call and pager duty (Amazon)
    \item
        Became a valuable team resource for Linux-specific and build-system related
        knowledge (Amazon)
    \item
        Interviewed candidates for open positions on the team regularly (Amazon)
    \item
        Mentored an intern and two new-hires (Amazon)
    \item
        Prominent member of the Sammamish Symphony Orchestra cello section.
    \item
        Leader for EPICS: Engineering Projects in Community Service "Judicial
        Database Systems" team.  The project won the 2004 EPISC I2P competition,
        leading to the first commercial company spin-off from an EPICS project.
        (Purdue)
    \item
        Assistant Principal Cellist in the Purdue Symphony Orchestra (Purdue)
    \end{list2}

    %____________________________________________________________________________________
    % Programming Expertise
    \section{\mysidestyle Programming Expertise} 
    \begin{list2}
    \item 
        Perl: 8 / 10, 3 years experience, 2 years development experience
    \item
        C++: 7 / 10, 3 years experience
    \item
        Java: 5 / 10, 2 years experience, 1 year development experience
    \item
        C: 5 / 10, 3 years experience
    \item
        Also fluent in Mason, Python, Motorola HC12 Assembly, Bash/Kornshell
        scripting, GNU Make, Mysql, Oracle PL/SQL, Ant, and hardware description
        languages.
    % TODO: add details about build system and web services expertise?
    \end{list2}

    %____________________________________________________________________________________
    % Interests
    \section{\mysidestyle Interests} 
    Open Source Software, Open Source Operating Systems specifically, processor
    architecture, networking, video games, classical music, and scientific
    pursuits.

    %____________________________________________________________________________________
    % References
    % TODO: format this nicer
    \section{\mysidestyle Technical References}
    \begin{list2}
        \item
        Ben Bernard - Senior Software Design Engineer, Amazon.com - 206-266-2407
    \end{list2}

    \vspace{2mm}

    \section{\mysidestyle Personal References}
    \begin{list2}
        \item
        R. Joseph Scott - Music Director and Conductor, Sammamish Symphony
        Orchestra - 206-323-2805
        \item
        Keith Amling - Software Design Engineer, Amazon.com - 206-434-0931
    \end{list2}

    {\sl More references available on request.}


%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

